---
title: "Sally the Congressperson: A Psycho- and Sociolinguistic Investigation into the Relationship Between Ideology, Gender, and Language: Final Production Model"
author: "B. Papineau"
date: "Autumn 2021"
output:
  html_notebook:
    toc: yes
    toc_float:
      collapsed: no
    number_sections: yes
    theme: journal
  html_document:
    toc: yes
    df_print: paged
---

# Introduction 
The code and information contained herein constitutes the complete write-up of the experiments I carried out for my first Qualifying Paper towards the PhD in Linguistics at Stanford University. The goal is to make this document both a dumping ground for my ideas while it is in progress, as well as, eventually, a publicly-available version of my Qualifying Paper, in the spirit of Open Science.

## Preliminaries 

### Setting up the Notebook

For this write-up and analysis, I require the following packages, loaded in here:

```{r echo=TRUE}
library(ggplot2) 
library(tidyverse) 
library(lme4) 
library(stringr)
library(languageR)
library(lmerTest)
library(reshape2)
library(grid)

source("helpers.R")
```

I also use a custom color palette, so I include the code for that here as well^[It is my hope and intention that this color palette be color-blind friendly. If you have accessibility concerns, please do not hesitate to reach out to me!].

```{r}
bran_palette = c("#7ae7e5", "#fe5f55", "#B2A6DE", "#14342b", "#69385c")

theme_set(theme_minimal())
```

### Frequency Data

We also need the frequency data!

```{r}
frequency <- read.csv("freq_vals.csv")
```

```{r}
lib_cols <- c('ABC','CNN','PBS','NBC','MSNBC','NPR','CBS')
```

```{r}
frequency <- frequency %>%
  mutate(total_left = rowSums(frequency[lib_cols])) %>%
  mutate(total_right = FOX) %>%
  mutate(all_wpm = ((total_left + total_right) / 121500000) * 1000000) %>%
  mutate(left_wpm = (total_left/109300000) * 1000000) %>%
  mutate(right_wpm = (total_right/12200000) * 1000000) %>%
  mutate(neutral_binary = ifelse(gender=="neutral",1,0)) %>%
  mutate(morph_type = ifelse(lexeme!= 'actor' & lexeme!= 'host' & lexeme !='hunter' & lexeme!= 'villain' & lexeme!= 'heir' & lexeme!= 'hero','compound','adoption')) %>% 
  rename(form = word) 
```

```{r}
frequency %>%
  group_by(lexeme)
```


Re-write frequency to avoid zero numbers!

```{r}
frequency[frequency == 0.00000000] <- 0.0001
```

Take log frequency of each media type.

```{r}
frequency <- frequency %>%
  mutate(log_right = log(right_wpm), log_left = log(left_wpm), log_all = log(all_wpm)) 
```

Create media difference 

```{r}
frequency <- frequency %>% 
  mutate(media_diff = log_left - log_right) %>%
  mutate(nonexistent = ifelse(media_diff == 0 & log_left < -4,"true","false")) %>%
  mutate(freq_gender = ifelse(form == "actress" | form == "anchorwoman" | form == "stewardess" | form == "businesswoman" | form == 'camerawoman' | form == 'congresswoman' | form == 'craftswoman' | form == 'crewwoman' | form == 'firewoman' | form == 'forewoman'  | form == 'heiress' | form == 'heroine' | form == 'hostess' | form == 'huntress' | form == 'laywoman' | form == 'policewoman' | form == 'saleswoman' | form == 'stuntwoman' | form == 'villainess' | form == 'weatherwoman',"female",ifelse(form == "anchor" | form == "flight attendant" | form == "businessperson" | form == 'camera operator' | form == 'congressperson' | form == 'craftsperson' | form == 'crewmember' | form == 'firefighter' | form == 'foreperson' | form == 'layperson' | form == 'police officer' | form == 'salesperson' | form == 'stunt double' | form == 'meteorologist',"neutral",ifelse(form == "anchorman" | form == "steward" | form == "businessman" | form == 'cameraman' | form == 'congressman' | form == 'craftsman' | form == 'crewman' | form == 'fireman' | form == 'foreman' | form == 'layman' | form == 'policeman' | form == 'salesman' | form == 'stuntman' | form == 'weatherman',"male",'neutral'))))
```


```{r}
frequency <- subset(frequency, select = -c(ABC,CNN,PBS,NBC,MSNBC,NPR,CBS,FOX))
```

```{r}
freq_log_all <- frequency %>% 
  select(lexeme,freq_gender,log_all) %>% 
  pivot_wider(names_from = freq_gender,values_from = log_all,names_prefix="log_all_")
```

```{r}
freq_log_right <- frequency %>% 
  select(lexeme,freq_gender,log_right) %>% 
  pivot_wider(names_from = freq_gender,values_from = log_right,names_prefix="log_right_")
```

```{r}
freq_log_left <- frequency %>% 
  select(lexeme,freq_gender,log_left) %>% 
  pivot_wider(names_from = freq_gender,values_from = log_left,names_prefix="log_left_")
```

```{r}
freq_lex <- left_join(freq_log_all,freq_log_right,by="lexeme")
```

```{r}
freq_lex <- left_join(freq_lex,freq_log_left,by="lexeme")
```

### Heavy Data Analysis; DANGER ZONE

```{r}
freq_lex <- freq_lex %>%
  mutate(morph_type = ifelse(lexeme!= 'actor' & lexeme!= 'host' & lexeme !='hunter' & lexeme!= 'villain' & lexeme!= 'heir' & lexeme!= 'hero','compound','adoption')) %>% 
  mutate(
    rel_fem_odds = log_all_neutral / log_all_female,
    rel_male_odds = case_when(
      morph_type == "adoption" ~ log_all_neutral / log_all_neutral,
      morph_type == "compound" ~ log_all_neutral / log_all_male
    )
  )
```



### Norming Data

And here is the norming data values:

```{r ECHO=TRUE}
norming_data <- read.csv("norming_data.csv") %>%
  filter(id!="example1") %>% # Will filter out non-critical trials, i.e. the example trial from the beginning of the experiment
  mutate(equalized_response = ifelse(scale=="FM",8-response,response)) %>% # This will render all data points on the same scale, as participants randomly received either "very likely a man" or "very likely a woman" as the left end of their response scale, with the other appearing at the right end
  mutate(orthog = ifelse(orthog=="sroceress","sorceress",orthog)) %>% # Fixes a typo
  mutate(id = ifelse(id=="Stunt_double","stunt double",id)) %>% # This, as well as all lines below it, convert compounds formed by spaces from their underscore forms to their spaced forms (e.g. police_officer -> Police officer)
  mutate(id = ifelse(id=="Police_officer","police officer",id)) %>%
  mutate(id = ifelse(id=="Flight_attendant","flight attendant",id)) %>%
  mutate(id = ifelse(id=="Anchor","anchor",id)) %>%
  mutate(id = ifelse(id=="Businessperson","businessperson",id)) %>%
   mutate(id = ifelse(id=="Camera","camera operator",id)) %>%
  mutate(id = ifelse(id=="Congressperson","congressperson",id)) %>%
  mutate(id = ifelse(id=="Craftsperson","craftsperson",id)) %>%
  mutate(id = ifelse(id=="Crewmember","crewmember",id)) %>%
  mutate(id = ifelse(id=="Firefighter","firefighter",id)) %>%
  mutate(id = ifelse(id=="Foreperson","foreperson",id)) %>%
  mutate(id = ifelse(id=="Layperson","layperson",id)) %>%
  mutate(id = ifelse(id=="Meteorologist","meteorologist",id)) %>%
  mutate(id = ifelse(id=="Salesperson","salesperson",id)) %>%
  mutate(id = ifelse(id=="Actor","actor",id)) %>%
  mutate(id = ifelse(id=="Heir","heir",id)) %>%
  mutate(id = ifelse(id=="Hero","hero",id)) %>%
  mutate(id = ifelse(id=="Host","host",id)) %>%
  mutate(id = ifelse(id=="Hunter","hunter",id)) %>%
  mutate(id = ifelse(id=="Villain","villain",id)) %>%
  mutate(orthog = ifelse(orthog=="airline steward","steward",orthog)) %>%
  mutate(orthog = ifelse(orthog=="airline stewardess","stewardess",orthog))
```

```{r ECHO=TRUE}
norming_exclusion <- norming_data %>% 
  filter(gender=="female") %>% 
  group_by(workerid) %>%
  summarize(female_mean = mean(equalized_response)) %>%
  unique() %>% 
  mutate(exclusion = female_mean < mean(female_mean) - 2*sd(female_mean)) %>%
  filter(exclusion==TRUE)
```

```{r ECHO=TRUE}
norming_data <- norming_data[!(norming_data$workerid %in% norming_exclusion$workerid),]
```

```{r}
norming_means <- norming_data %>%
  filter(neutral_morh !="male_adoption") %>%
  group_by(orthog,id) %>%
  summarise(indi_mean = mean(equalized_response), trial_count=n()) %>%
  rename(form = orthog) %>%
  rename(lexeme =id)
```

```{r}
norming_adoptions <- norming_data %>%
  filter(neutral_morh == "male_adoption") %>%
  group_by(orthog) %>%
  summarise(indi_mean = mean(equalized_response), trial_count=n()) %>%
  mutate(lexeme = ifelse(orthog=="actress","actor",ifelse(orthog=="heiress","heir",ifelse(orthog=="heroine","hero",ifelse(orthog=="hostess","host",ifelse(orthog=="huntress","hunter",ifelse(orthog=="villainess","villain",orthog))))))) %>%
    rename(form = orthog)
```

```{r}
norming_adoptions <- norming_adoptions[, c("lexeme", "form", "indi_mean", "trial_count")]
```

```{r}
norming_means <- rbind(norming_means,norming_adoptions) %>%
  rename(lexeme_norm = lexeme)
```

```{r include=FALSE}
later_criticals <- c("actor","anchor","businessperson","camera operator","congressperson","craftsperson","crewmember","firefighter","flight attendant","foreperson","heir","hero","host","hunter","layperson","meteorologist","police officer","salesperson","stunt double","villain")
```

```{r include=FALSE}
norming_means <- norming_means[(norming_means$lexeme_norm %in% later_criticals),]
```

**Neutrals Only**

```{r}
norming_means_neutral <- norming_data %>%
  filter(gender=="neutral") %>%
  filter(neutral_morh !="male_adoption") %>%
  group_by(orthog,id) %>%
  summarise(indi_mean = mean(equalized_response), trial_count=n()) %>%
  rename(form = orthog) %>%
  rename(lexeme =id)
```

```{r}
norming_adoptions_neutral <- norming_data %>%
  filter(gender=="neutral") %>%
  filter(neutral_morh == "male_adoption") %>%
  group_by(orthog) %>%
  summarise(indi_mean = mean(equalized_response), trial_count=n()) %>%
  mutate(lexeme = ifelse(orthog=="actress","actor",ifelse(orthog=="heiress","heir",ifelse(orthog=="heroine","hero",ifelse(orthog=="hostess","host",ifelse(orthog=="huntress","hunter",ifelse(orthog=="villainess","villain",orthog))))))) %>%
    rename(form = orthog)
```

```{r}
norming_adoptions_neutral <- norming_adoptions_neutral[, c("lexeme", "form", "indi_mean", "trial_count")]
```

```{r}
norming_means_neutral <- rbind(norming_means_neutral,norming_adoptions_neutral)
```

```{r include=FALSE}
norming_means_neutral <- norming_means_neutral[(norming_means_neutral$lexeme %in% later_criticals),]
```


# Analysis

## Data Read-in

```{r}
prod_data <- read.csv("production_data.csv")
```

## Exclusions

```{r}
prod_exclusion <- prod_data %>% filter(name=='attention') %>%
  group_by(workerid) %>%
  summarise(accuracy = mean(correct)) %>%
  mutate(exclude = ifelse(accuracy < 0.80,'Yes','No')) %>%
  filter(exclude == "Yes")
```

```{r}
prod_data <- prod_data[!(prod_data$workerid %in% prod_exclusion$workerid),]
```

## Additional Information 

```{r}
gender_transcendence_cols <- c('subject_information.gender_q1','subject_information.gender_q2','subject_information.gender_q3','subject_information.gender_q4','subject_information.gender_q5')

gender_linked_cols <- c('subject_information.gender_q6','subject_information.gender_q7','subject_information.gender_q8','subject_information.gender_q9','subject_information.gender_q10','subject_information.gender_q11','subject_information.gender_q12','subject_information.gender_q13')
```

```{r}
prod_data <- prod_data %>%
  mutate(gender_trans = 100 - (rowMeans(prod_data[gender_transcendence_cols]))) %>%
  mutate(gender_link = rowMeans(prod_data[gender_linked_cols])) 

gender_all = c('gender_trans','gender_link')

prod_data <- prod_data %>%
  mutate(gender_total = rowMeans(prod_data[gender_all]))
``` 

```{r}
prod_data <- prod_data %>%
  filter(type == "critical") %>%
  mutate(response_gender = ifelse(response == "actress" | response == "anchorwoman" | response == "stewardess" | response == "businesswoman" | response == 'camerawoman' | response == 'congresswoman' | response == 'craftswoman' | response == 'crewwoman' | response == 'firewoman' | response == 'forewoman'  | response == 'heiress' | response == 'heroine' | response == 'hostess' | response == 'huntress' | response == 'laywoman' | response == 'policewoman' | response == 'saleswoman' | response == 'stuntwoman' | response == 'villainess' | response == 'weatherwoman',"female",ifelse(response == "anchor" | response == "flight attendant" | response == "businessperson" | response == 'camera operator' | response == 'congressperson' | response == 'craftsperson' | response == 'crewmember' | response == 'firefighter' | response == 'foreperson' | response == 'layperson' | response == 'police officer' | response == 'salesperson' | response == 'stunt double' | response == 'meteorologist',"neutral",ifelse(response == "anchorman" | response == "steward" | response == "businessman" | response == 'cameraman' | response == 'congressman' | response == 'craftsman' | response == 'crewman' | response == 'fireman' | response == 'foreman' | response == 'layman' | response == 'policeman' | response == 'salesman' | response == 'stuntman' | response == 'weatherman',"male",'male/neutral')))) %>%
  mutate(congruency = ifelse(gender == response_gender,"true","false")) %>%
  mutate(incongruent = ifelse(gender == "male" & response_gender == "female","incongruent_mtf",ifelse(gender == "female" & response_gender == "male","incongruent_ftm","real"))) %>%
  mutate(neutrality = ifelse(response_gender == "neutral","true","false"))%>%
  mutate(morph_type = ifelse(lexeme!= 'actor' & lexeme!= 'host' & lexeme !='hunter' & lexeme!= 'villain' & lexeme!= 'heir' & lexeme!= 'hero','compound','adoption')) %>%
  mutate(poli_party = ifelse(subject_information.party_alignment == 1 | subject_information.party_alignment == 2,'Republican',ifelse(subject_information.party_alignment == 4 | subject_information.party_alignment == 5,'Democrat','Non-Partisan'))) %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>% 
  mutate(young_old = ifelse(subject_information.age > 40,"old","young")) %>%
  rename(form = response)
```

**Joining independent data**
Now that we have this information, we want to left join our frequency information so that we can use it in later analyses. We begin by adding the norming values' means, of all forms.

```{r}
final_prod <- left_join(prod_data,norming_means,by="form")
```

Now we can add the frequency data as well, by form. 

```{r}
final_prod <- left_join(final_prod,freq_lex,by="lexeme")
```

Now we can add additional lexeme-level norming information for the neutral forms, so that we can tackle the question of what role real-world expectations have on processing times. 

```{r}
final_prod <- left_join(final_prod,norming_means_neutral,by="lexeme")
```

```{r}
final_prod <- subset(final_prod, select = -c(form.y,trial_count.y,trial_count.x,error,subject_information.comments,subject_information.asses,subject_information.enjoyment,subject_information.gender_q1,subject_information.gender_q2,subject_information.gender_q3,subject_information.gender_q4,subject_information.gender_q5,subject_information.gender_q6,subject_information.gender_q7,subject_information.gender_q8,subject_information.gender_q9,subject_information.gender_q10,subject_information.gender_q11,subject_information.gender_q12,subject_information.gender_q13,lexeme_norm)) %>%
  rename(form_norm = indi_mean.x, lexeme_norm = indi_mean.y, form = form.x)
```

### Heavy data manipulation; DANGER ZONE

```{r}
final_prod <- final_prod %>%
  mutate(log_odds = case_when(
    gender == "male" ~ rel_male_odds,
    gender == "female" ~ rel_fem_odds
  )) %>% 
  mutate(c_gender_total = scale(gender_total,scale=FALSE)) %>%
  mutate(c_gender_trans = scale(gender_trans,scale=FALSE)) %>%
  mutate(c_gender_link = scale(gender_link,scale=FALSE))
```


```{r}
final_prod <- final_prod %>%
  mutate(poli_party = factor(poli_party,ordered = FALSE)) %>%
  mutate(trial_gender = factor(gender,ordered = FALSE)) %>% 
  mutate(c_trial_gender = scale(as.numeric(trial_gender),scale=FALSE))
```

```{r}
final_prod$poli_party = relevel(final_prod$poli_party, ref="Non-Partisan")
final_prod$trial_gender = relevel(final_prod$trial_gender, ref="male")
```

```{r}
prod_ultimate_model <- lmer(response_neutral~c_trial_gender*c_gender_total:subject_information.age + log_odds*poli_party*subject_information.age +log_odds:c_trial_gender + c_gender_total + (1 |workerid) + (1 + trial_gender|lexeme),data=final_prod)
```

```{r}
summary(prod_ultimate_model)
```



# Incongruent Response Analysis (Auxiliary)

```{r}
incongruent <- final_prod %>%
  filter(incongruent == "incongruent_ftm" | incongruent == "incongruent_mtf")
```

```{r}
table(incongruent$response_gender,incongruent$gender,incongruent$morph_type,incongruent$lexeme)
```

```{r}
incongruent%>%
  group_by(workerid,incongruent) %>%
  count() %>%
  arrange(n) %>%
  ggplot(aes(x=n,fill=incongruent)) + 
  geom_histogram()
```

