---
title: "Papineau Qualifying Paper 1: Norming Study Supplementary Materials"
author: "B. Papineau"
date: "Last Revised: Wednesday, December 22, 2021"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: no
    number_sections: yes
    theme: journal
    df_print: paged
  html_notebook:
    toc: yes
    toc_float:
      collapsed: no
    number_sections: yes
    theme: journal
---
---

# Introduction

This document contains supplementary material related to my first Qualifying Paper towards the PhD in Linguistics at Stanford University. This is a living document (see last revision date above), but contains the methods and results of my norming study on the gendered interpretations of gender-marked role titles in English.\par 

```{r include=FALSE}
library(ggplot2) 
library(gt)
library(webshot)
library(tidyverse) 
library(lme4) 
library(stringr)
library(languageR)
library(lmerTest)
library(reshape2)
library(grid)

source("helpers.R")

bran_palette = c("#7ae7e5", "#fe5f55", "#B2A6DE", "#14342b", "#69385c")
sec_palette = c("#3d405b","#e07a5f","#81b29a","f2cc8f")

theme_set(theme_minimal())

dodge = position_dodge(0.9)

ad_lexemes <- c("actor","emperor","god","newsboy","sorcerer","usher","host","hunter","villain","heir","hero")

`%notin%` <- Negate(`%in%`)
```

## Methods

### Participants

100 participants were recruited through the online recruitment platform [Prolific](prolific.co.uk). All participants were self-identified L1 English speakers and were born and resided in the United States at the time of participation. None of the participants had participated in the 4-person pilot of the norming study, and the pilot data is not reported here. 

All participants, regardless of their data's final inclusion in the analysis, were compensated \$2.00 for their partaking in the study. The average completion time for the task was 4.353 minutes, which resulted in an average payout of \$31.85/hr. 

### Experiment

A link to the experiment can be found [here](https://branpap.github.io/gender_processing/experiments/norming_study_one/experiment.html), and is available for the keen reader to click through; results are not stored in any way.

Participants were presented with 39 sentence frames of the structure "Someone is a [role title]", and were asked to indicate on a seven-point Likert scale how likely they thought it was that the 'someone' in question was male or female. The Likert scales were randomized between participants with regard to which end of the scale represented a (fe)male response. In each sentence, participants were presented with one of 39 role titles in one of its gendered permutations, such that no participant saw the same lexeme multiple times with different gender markings. All participants saw 13 items of each gender (male/female/neutral). 

Role titles were selected from a variety of online guides on avoiding gendered language in English. Of the 39 role titles included, 11 made binary gender distinctions between male and female forms (e.g. *villain* vs. *villainess*), while the remaining 28 make ternary gender distinctions with an additional neutral manifestation (e.g. *congressman* vs. *congresswoman* vs. *congressperson*). The norming items are presented in the table below. 

   

```{r include=FALSE}
norm_stims <- read.csv("norm_stims.csv") %>%
  mutate(Neutral = ifelse(Male == Neutral,"---",paste(Lexeme)))
```

```{r echo=FALSE}
norm_stims %>%
  gt(rowname_col = "Lexeme") %>% 
  tab_stubhead(label="Lexeme") %>%
  tab_header(
    title="Norming Stimuli Items",
    subtitle="Presented by lexeme & gendered forms"
  ) %>%
  tab_spanner(
    label = "Gendered Forms",
    columns = c(Male,Female,Neutral)
  ) 
```

```{r include=FALSE}
norm_stims %>%
  gt(rowname_col = "Lexeme") %>% 
  tab_stubhead(label="Lexeme") %>%
  tab_header(
    title="Norming Stimuli Items",
    subtitle="Presented by lexeme & gendered forms"
  ) %>%
  tab_spanner(
    label = "Gendered Forms",
    columns = c(Male,Female,Neutral)
  ) %>%
  gtsave(
    "norm_stims_table.png",
    path="/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper/figures/"
  )
```


### Exclusions 
Because we expect the female-marked forms to be rated near to ceiling as female-referring, participants were excluded from analysis if their mean score for their female items were less than two standard deviations away from the group mean. This resulted in an exclusion of 11 participants, for a total datset of 89 participants and 3,471 observations. 

## Results

```{r include=FALSE}
norming_data <- read.csv("norming_data.csv") %>%
  filter(id!="example1") %>% # Will filter out non-critical trials, i.e. the example trial from the beginning of the experiment
  mutate(equalized_response = ifelse(scale=="FM",8-response,response)) %>% # This will render all data points on the same scale, as participants randomly received either "very likely a man" or "very likely a woman" as the left end of their response scale, with the other appearing at the right end
  mutate(orthog = ifelse(orthog=="sroceress","sorceress",orthog)) %>% # Fixes a typo
  mutate(id = ifelse(id=="Stunt_double","Stunt double",id)) %>% # This, as well as all lines below it, convert compounds formed by spaces from their underscore forms to their spaced forms (e.g. police_officer -> Police officer)
  mutate(id = ifelse(id=="Restaurant_server","Restaurant server",id)) %>%
  mutate(id = ifelse(id=="Police_officer","Police officer",id)) %>%
  mutate(id = ifelse(id=="Door_attendant","Door attendant",id)) %>%
  mutate(id = ifelse(id=="Flight_attendant","Flight attendant",id)) %>%
  mutate(id = ifelse(id=="Garbage_Collector","Garbage collector",id)) %>%
  mutate(id = ifelse(id=="Mail_Carrier","Mail carrier",id)) %>%
  mutate(id = ifelse(id=="Maintenance_Person","Maintenance person",id)) %>%
  mutate(id = ifelse(id=="Paper_carrier","Paper carrier",id)) 
```


```{r include=FALSE}
norming_exclusion <- norming_data %>% 
  filter(gender=="female") %>% 
  group_by(workerid) %>%
  summarize(female_mean = mean(equalized_response)) %>%
  unique() %>% 
  mutate(exclusion = female_mean < mean(female_mean) - 2*sd(female_mean)) %>%
  filter(exclusion==TRUE)

norming_data <- norming_data[!(norming_data$workerid %in% norming_exclusion$workerid),]
```

### Means by item, inclusive

Presented here are the mean evaluations of all 39 lexemes in each of their gendered permutations. A score of 7 means that the variant was evaluated as being extremely likely to be referring to a female, while a score of 1 indicates that the variant was taken to refer to a male. A midling score reflects an ambiguous (or potentially non-binary) referent. 

```{r include=FALSE}
norming_means <- norming_data %>%
  mutate(young_old = ifelse(subject_information.age > 40,"old","young")) %>% 
  mutate(morphology = case_when(
    neutral_morh != "male_adoption" ~ "compound", 
    TRUE ~ "adoption"
  )) %>% 
  mutate(gender = case_when(
    gender == "male" & morphology == "adoption" ~ "neutral",
    TRUE ~ paste(gender)
  )) %>% 
  group_by(id,gender) %>%
  summarise(indi_mean = mean(equalized_response),
            trial_count=n(),
            CI.Low = ci.low(equalized_response),
            CI.High = ci.high(equalized_response)
            ) %>% 
  mutate(YMin = indi_mean - CI.Low,
         YMax = indi_mean + CI.High)
```

norming_means <- norming_data %>% 
  mutate(morphology = case_when(
    neutral_morh != "male_adoption" ~ "compound", 
    TRUE ~ "adoption"
  )) %>% 
  group_by(id,gender,morphology) %>% 
  summarize(indi_mean = mean(equalized_response),
            trial_count=n(),
            CI.Low = ci.low(equalized_response),
            CI.High = ci.high(equalized_response)
            ) %>% 
  spread(gender,indi_mean) %>% 
  mutate(true_neutral = case_when(
    morphology == "Adoption" ~ (male + neutral)/2,
    TRUE ~ neutral
  )) %>% 
  gather(gender, value, female:true_neutral, factor_key = TRUE) %>% 
  mutate(temp = case_when(
    morphology == "adoption" & gender == "male" ~ "del",
    TRUE ~ 'no',
  )) %>% 
  filter(gender != "neutral") %>% 
  filter(temp == 'no') %>% 
  mutate(gender = case_when(
    gender == "true_neutral" ~ "neutral",
    TRUE ~ paste(gender)
  )) %>% 
  select(-temp)

```{r include=FALSE}
text_high <- textGrob("Female", gp=gpar(fontsize=10, fontface="bold"))
text_low <- textGrob("Male", gp=gpar(fontsize=10, fontface="bold"))
```

```{r echo=FALSE}
ggplot(norming_means, aes(x=id, y=indi_mean, color=gender)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = YMin, ymax=YMax),
                width=0.25) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=45, hjust=1, size=8)) + 
  labs(x="Ungendered Lexical Item", y="Mean Rating", color = "Gender of Form Seen") + 
  scale_color_manual(values = sec_palette, limits=c("male","female","neutral")) + 
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  annotation_custom(text_high,xmin=-1.3,xmax=-1.3,ymin=6.8,ymax=6.8) + 
  annotation_custom(text_low,xmin=-1,xmax=-1,ymin=1,ymax=1) + 
  coord_cartesian(clip = "off") + 
  theme(legend.position = "top")
```

```{r include=FALSE}
ggsave("norming-means-all.png", width=7,height=4, path="/Users/branpap/Desktop/gender_ideology/talks_and_papers/qp_paper/figures/")
```


### Means by item, subsequent experiments only

This graph presents the same values, but includes only the lexical items which were used as critical items in the subsequent experiments. 

```{r include=FALSE}
later_criticals <- c("Actor","Anchor","Businessperson","Camera operator","Congressperson","Craftsperson","Crewmember","Firefighter","Flight attendant","Foreperson","Heir","Hero","Host","Hunter","Layperson","Meteorologist","Police officer","Salesperson","Stunt double","Villain")
```

```{r include=FALSE}
critical_means <- norming_means[(norming_means$id %in% later_criticals),]
```


```{r echo=FALSE}
critical_means %>%
  ggplot(aes(x=id, y=indi_mean, color=gender)) + 
  geom_point() + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=45, hjust=1, size=8)) + 
  labs(x="Ungendered Lexical Item", y="Mean Rating", color = "Gender of Form Seen", title="Mean Gender Rating by Ungendered Form and Gender Seen") + 
  scale_color_manual(values = bran_palette) + 
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  annotation_custom(text_high,xmin=-0.3,xmax=-0.3,ymin=6.8,ymax=6.8) + 
  annotation_custom(text_low,xmin=-0.3,xmax=-0.3,ymin=1,ymax=1) + 
  coord_cartesian(clip = "off")
```


```{r include=FALSE}
ggsave("norming_means_subsequent.png", width=7,height=4, path="/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper/figures/")
```


```{r include=FALSE}
norming_means_av <- norming_data %>%
  mutate(young_old = ifelse(subject_information.age > 40,"old","young")) %>% 
  group_by(gender,young_old) %>%
  summarise(indi_mean = mean(equalized_response),
            trial_count=n(),
            CI.Low = ci.low(equalized_response),
            CI.High = ci.high(equalized_response)
            ) %>% 
  mutate(YMin = indi_mean - CI.Low,
         YMax = indi_mean + CI.High)
```

```{r}
norming_means_av %>% 
  ggplot(aes(x=gender,y=indi_mean)) + 
  geom_bar(stat='identity') + 
  facet_wrap(~young_old)
```


```{r include=FALSE}
norming_data %>%
  mutate(young_old = ifelse(subject_information.age > 40,"old","young")) %>% 
  mutate(morphology = case_when(
    neutral_morh != "male_adoption" ~ "compound", 
    TRUE ~ "adoption"
  )) %>% 
  mutate(gender = case_when(
    gender == "male" & morphology == "adoption" ~ "neutral",
    TRUE ~ paste(gender)
  )) %>% 
  group_by(gender) %>%
  summarise(indi_mean = mean(equalized_response),
            trial_count=n(),
            CI.Low = ci.low(equalized_response),
            CI.High = ci.high(equalized_response)
            ) %>% 
  mutate(YMin = indi_mean - CI.Low,
         YMax = indi_mean + CI.High) %>% 
  ggplot(aes(x=gender,y=indi_mean,fill=gender)) +
  geom_bar(stat="identity") + 
  geom_errorbar(aes(ymin = YMin, ymax=YMax),
                width=0.25) + 
  theme(legend.position = "none")  + 
  labs(x="Item Gender", y="Mean Rating", color = "Gender of Form Seen") + 
  scale_fill_manual(values = sec_palette, limits=c("male","female","neutral")) 
```
