---
title: "'Sally the Congressperson': Interlocutor Agency Modulates the Role of Subjective Social Beliefs in Linguistic Processes"
author: "Bran Papineau"
date: "5/23/2022"
output: ioslides_presentation
---

```{r include=FALSE}
library(tidyverse)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

- Background
- Research Question
- Study One: Processing
  - Methods
  - Results
- Study Two: Production
  - Methods
  - Results
-Discussion
-Conclusion

# Background

## Background: 

## Background: Surprisal

# Research Question

# Something

# The Studies

# Study One: Processing

## Methods

- n=279 English-speaking participants recruited through Prolific 
  - Exclusions (failure on 85% of attention checks): n=19
- Web-based self-paced reading task
  - Reading time is proportional to processing difficulty
- Post-experimental survey of gender ideology (Baber & Tucker 2008)
  - 13 questions, 1-100 sliding scale
  - 0 = most gender progressive | 100 = most gender conservative


## Methods: Experimental Design

## Results

# Study Two: Production

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

