---
title: "Papineau QP1 - Production Analysis"
author: "B. Papineau"
date: "Autumn 2021"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
    toc_float:
      collapsed: no
    number_sections: yes
    theme: journal
---

# Preliminaries

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggpubr)

source("helpers.R")
```

```{r}
bran_palette = c("#7ae7e5","#B2A6DE", "#fe5f55", "#14342b", "#69385c")

theme_set(theme_minimal())
```

```{r}
lex_freqs <- read.csv("freq_preped.csv") %>%
  mutate(left_surprisal = (-log(mean_left_neutral))/(-log(mean_left_gendered))) %>%
  mutate(right_surprisal = (-log(mean_right_neutral))/(-log(mean_right_gendered)))
```

```{r}
lex_freqs[lex_freqs == 0.00000000] <- 0.00000001
lex_freqs[lex_freqs == "-Inf"] <- -999999999
lex_freqs[lex_freqs == "Inf"] <- 999999999
```

```{r}
gender_transcendence_cols <- c('subject_information.gender_q1','subject_information.gender_q2','subject_information.gender_q3','subject_information.gender_q4','subject_information.gender_q5')

gender_linked_cols <- c('subject_information.gender_q6','subject_information.gender_q7','subject_information.gender_q8','subject_information.gender_q9','subject_information.gender_q10','subject_information.gender_q11','subject_information.gender_q12','subject_information.gender_q13')
```

# Analysis

## Data Read-in

```{r}
prod_data <- read.csv("production_data.csv")
```

## Exclusions

```{r}
prod_exclusion <- prod_data %>% filter(name=='attention') %>%
  group_by(workerid) %>%
  summarise(accuracy = mean(correct)) %>%
  mutate(exclude = ifelse(accuracy < 0.80,'Yes','No')) %>%
  filter(exclude == "Yes")
```

```{r}
prod_data <- prod_data[!(prod_data$workerid %in% prod_exclusion$workerid),]
```

## Additional Information 

```{r}
prod_data <- prod_data %>%
  mutate(gender_trans = 100 - (rowMeans(prod_data[gender_transcendence_cols]))) %>%
  mutate(gender_link = rowMeans(prod_data[gender_linked_cols])) 

gender_all = c('gender_trans','gender_link')

prod_data <- prod_data %>%
  mutate(gender_total = rowMeans(prod_data[gender_all]))
``` 

```{r}
prod_data <- prod_data %>%
  filter(type == "critical") %>%
  mutate(response_gender = ifelse(response == "actress" | response == "anchorwoman" | response == "stewardess" | response == "businesswoman" | response == 'camerawoman' | response == 'congresswoman' | response == 'craftswoman' | response == 'crewwoman' | response == 'firewoman' | response == 'forewoman'  | response == 'heiress' | response == 'heroine' | response == 'hostess' | response == 'huntress' | response == 'laywoman' | response == 'policewoman' | response == 'saleswoman' | response == 'stuntwoman' | response == 'villainess' | response == 'weatherwoman',"female",ifelse(response == "anchor" | response == "flight attendant" | response == "businessperson" | response == 'camera operator' | response == 'congressperson' | response == 'craftsperson' | response == 'crewmember' | response == 'firefighter' | response == 'foreperson' | response == 'layperson' | response == 'police officer' | response == 'salesperson' | response == 'stunt double' | response == 'meteorologist',"neutral",ifelse(response == "anchorman" | response == "steward" | response == "businessman" | response == 'cameraman' | response == 'congressman' | response == 'craftsman' | response == 'crewman' | response == 'fireman' | response == 'foreman' | response == 'layman' | response == 'policeman' | response == 'salesman' | response == 'stuntman' | response == 'weatherman',"male",'male/neutral')))) %>%
  mutate(congruency = ifelse(gender == response_gender,"true","false")) %>%
  mutate(neutrality = ifelse(response_gender == "neutral","true","false"))%>%
  mutate(morph_type = ifelse(lexeme!= 'actor' & lexeme!= 'host' & lexeme !='hunter' & lexeme!= 'villain' & lexeme!= 'heir' & lexeme!= 'hero','compound','adoption')) %>%
  mutate(poli_party = ifelse(subject_information.party_alignment == 1 | subject_information.party_alignment == 2,'Republican',ifelse(subject_information.party_alignment == 4 | subject_information.party_alignment == 5,'Democrat','Non-Partisan'))) %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0))
```

```{r include=FALSE}
norming_data <- read.csv("norming_data.csv") %>%
  filter(id!="example1") %>% # Will filter out non-critical trials, i.e. the example trial from the beginning of the experiment
  mutate(equalized_response = ifelse(scale=="FM",8-response,response)) %>% # This will render all data points on the same scale, as participants randomly received either "very likely a man" or "very likely a woman" as the left end of their response scale, with the other appearing at the right end
  mutate(orthog = ifelse(orthog=="sroceress","sorceress",orthog)) %>% # Fixes a typo
  mutate(id = ifelse(id=="Stunt_double","stunt double",id)) %>% # This, as well as all lines below it, convert compounds formed by spaces from their underscore forms to their spaced forms (e.g. police_officer -> Police officer)
  mutate(id = ifelse(id=="Police_officer","police officer",id)) %>%
  mutate(id = ifelse(id=="Flight_attendant","flight attendant",id)) %>%
  mutate(id = ifelse(id=="Anchor","anchor",id)) %>%
  mutate(id = ifelse(id=="Businessperson","businessperson",id)) %>%
   mutate(id = ifelse(id=="Camera","camera operator",id)) %>%
  mutate(id = ifelse(id=="Congressperson","congressperson",id)) %>%
  mutate(id = ifelse(id=="Craftsperson","craftsperson",id)) %>%
mutate(id = ifelse(id=="Crewmember","crewmember",id)) %>%
  mutate(id = ifelse(id=="Firefighter","firefighter",id)) %>%
  mutate(id = ifelse(id=="Foreperson","foreperson",id)) %>%
  mutate(id = ifelse(id=="Layperson","layperson",id)) %>%
  mutate(id = ifelse(id=="Meteorologist","meteorologist",id)) %>%
  mutate(id = ifelse(id=="Salesperson","salesperson",id)) 
```

```{r include=FALSE}
norming_exclusion <- norming_data %>% 
  filter(gender=="female") %>% 
  group_by(workerid) %>%
  summarize(female_mean = mean(equalized_response)) %>%
  unique() %>% 
  mutate(exclusion = female_mean < mean(female_mean) - 2*sd(female_mean)) %>%
  filter(exclusion==TRUE)

norming_data <- norming_data[!(norming_data$workerid %in% norming_exclusion$workerid),]
```

```{r include=FALSE}
norming_means <- norming_data %>%
  group_by(id,gender,orthog) %>%
  summarise(indi_mean = mean(equalized_response), trial_count=n()) %>%
  rename(lexeme = id) %>%
  filter(gender=="neutral")
```

```{r}
join_test <- merge(prod_data,norming_means,by="lexeme")
join_test <- merge(join_test,lex_freqs,by="lexeme")
```

```{r}
prod_data_means <- prod_data %>%
  filter(!is.na(poli_party)) %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="") %>%
  group_by(gender,workerid,poli_party,subject_information.gender,subject_information.age,subject_information.education,gender_total) %>%
  summarise(proportion = mean(response_neutral)) 
```

## Visualizations 

### Gender of Response by Political Alignment and Gender Ideology

```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="" & morph_type=="compound") %>%
  group_by(gender,gender_trans,poli_party) %>%
  summarise(proportion = mean(response_neutral)) %>%
  ggplot(aes(x=gender_trans, y=proportion, color=gender)) +
    geom_point() + 
    geom_smooth() + 
    scale_color_manual(values = bran_palette) +
    facet_wrap(~poli_party) + 
    labs(x="Gender Ideology Score", y="Proportion of Gender Neutral Responses",color="Gender of Name Seen") + 
    theme(text=element_text(size=15))
```

```{r}
ggsave("prod_neutral_poli.png", width=10,height=5,path='/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper/figures')
``` 

```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="") %>%
  group_by(gender,subject_information.age,poli_party) %>%
  summarise(proportion = mean(response_neutral)) %>%
  ggplot(aes(x=subject_information.age, y=proportion, color=gender)) +
    geom_point() + 
    geom_smooth() + 
    scale_color_manual(values = bran_palette) 
```

### Gender by Gender, no Ideology

```{r}
prod_data %>%
  filter(morph_type =="compound") %>%
  ggplot(aes(x=gender, fill=response_gender)) + 
  geom_bar(position="fill") + 
  scale_fill_manual(values = bran_palette) + 
  labs(x="Stimulus Gender", fill="Gender of Response", y="Proportion of Responses", title="Gender of Response by Gender of Stimulus Name") +
  theme_minimal()
```

### Proportion of Neutral Responses by Morphological Type

```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  mutate(response_neutral = ifelse(response_gender == "neutral" | response_gender == "male/neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="") %>%
  group_by(morph_type) %>%
  summarize(mean_prop = mean(response_neutral), CI.Low = ci.low(response_neutral), CI.High = ci.high(response_neutral)) %>%
  mutate(YMin = mean_prop - CI.Low, YMax = mean_prop + CI.High) %>%
  ggplot(aes(x=morph_type,y=mean_prop, fill=morph_type)) + 
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25) + 
  labs(x="Morphological Process", y="Mean Proportion of Neutral Responses") + 
  theme(text=element_text(size=16)) + 
  theme(axis.text.x = element_text(angle=5, vjust = .7)) + 
  scale_fill_manual(values = bran_palette) +
  theme(legend.position = "none")
```

```{r}
ggsave("prod_neutral_morph_bar.png", width=7, height=5,path='/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper/figures')
```

### Proportion of Neutral Responses by Political Ideology and Gender

```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  filter(morph_type == "compound") %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="") %>%
  #filter(poli_party != "Non-Partisan") %>%
  group_by(gender,poli_party) %>%
  summarize(mean_prop = mean(response_neutral), CI.Low = ci.low(response_neutral), CI.High = ci.high(response_neutral)) %>%
  mutate(YMin = mean_prop - CI.Low, YMax = mean_prop + CI.High) %>%
  ggplot(aes(x=gender,y=mean_prop,fill=gender)) + 
  geom_bar(stat='identity') + 
  geom_point(data=prod_data_means, aes(x=gender,y=proportion),alpha=0.15, position="jitter") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25) + 
  facet_wrap(~ poli_party) + 
  theme_bw() + 
  labs(x="Stimulus Gender", y="Mean Proportion of Neutral Responses",title="Neutral Responses by Stimuli Gender") + 
  theme(text=element_text(size=16)) + 
  theme(axis.text.x = element_text(angle=5, vjust = .7)) + 
  scale_fill_manual(values = bran_palette) +
  theme(legend.position = "none")
```

```{r}
ggsave("prod_neutral_gender_bar_nonmean.png", width=7, height=5,path='/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper/figures')
```

```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  filter(morph_type == "compound") %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="") %>%
  #filter(poli_party != "Non-Partisan") %>%
  group_by(gender,poli_party) %>%
  summarize(mean_prop = mean(response_neutral), CI.Low = ci.low(response_neutral), CI.High = ci.high(response_neutral)) %>%
  mutate(YMin = mean_prop - CI.Low, YMax = mean_prop + CI.High) %>%
  ggplot(aes(x=poli_party,y=mean_prop,fill=poli_party)) + 
  geom_bar(stat='identity') + 
  geom_point(data=prod_data_means, aes(x=poli_party,y=proportion),alpha=0.15, position="jitter") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25) + 
  facet_wrap(~ gender) + 
  theme_bw() + 
  labs(x="Participant Political Party", y="Mean Proportion of Neutral Responses",title="Neutral Responses by Stimuli Gender") + 
  theme(text=element_text(size=16)) + 
  theme(axis.text.x = element_text(angle=5, vjust = .7)) + 
  scale_fill_manual(values = bran_palette) +
  theme(legend.position = "none")
```
```{r}
ggsave("prod_neutral_poli_bar_nonmean.png", width=7, height=5,path='/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper/figures')
```

### Ideology by Political Party

```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  #filter(poli_party != "Non-Partisan") %>%
  group_by(poli_party) %>%
  summarize(mean_ideo = mean(gender_total), CI.Low = ci.low(gender_total), CI.High = ci.high(gender_total)) %>%
  mutate(YMin = mean_ideo - CI.Low, YMax = mean_ideo + CI.High) %>%
  ggplot(aes(x=poli_party,y=mean_ideo,fill=poli_party)) + 
  geom_bar(stat='identity') + 
  #geom_point(data=prod_data, aes(x=poli_party,y=gender_total),alpha=0.15, position="jitter") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25) + 
  theme_bw() + 
  labs(x="Participant Political Party", y="Mean Gender Ideology") + 
  theme(text=element_text(size=16)) + 
  theme(axis.text.x = element_text(angle=5, vjust = .7)) + 
  scale_fill_manual(values = bran_palette) +
  theme(legend.position = "none")
```

```{r}
ggsave("prod_ideology_party.png", width=7, height=5,path='/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper/figures')
```

### Individual Compounds 

```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  filter(morph_type == "compound") %>%
  mutate(response_neutral = ifelse(response_gender == "neutral" | response_gender == "male/neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="") %>%
  group_by(gender,lexeme,poli_party,subject_information.gender) %>%
  summarise(proportion = mean(response_neutral)) %>%
  group_by(gender,lexeme) %>%
  summarize(mean_prop = mean(proportion), CI.Low = ci.low(proportion), CI.High = ci.high(proportion)) %>%
  mutate(YMin = mean_prop - CI.Low, YMax = mean_prop + CI.High) %>%
  ggplot(aes(x=gender,y=mean_prop,fill=gender)) + 
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25) + 
  facet_wrap(~lexeme) + 
  theme(legend.position = "none") + 
  labs(x="Participant Political Party", y="Mean Proportion of Gender-Neutral Responses",title="Proportions of Neutral Responses by Stimuli Gender", fill="Political Party") + 
  theme(text=element_text(size=16)) + 
  theme(axis.text.x = element_text(angle=20)) +
  theme_grey() 
```

## Models

```{r}
prod_data_compounds <- prod_data %>%
  filter(morph_type == "compound") %>%
  mutate(cgender_total = scale(gender_total)) %>%
  mutate(response_congruency = as.numeric(ifelse(congruency=="true","1","0"))) %>%
  mutate(cage = scale(subject_information.age)) %>%
  mutate(neutrality_binary = ifelse(neutrality=="true",1,0))
```

```{r}
final_dat <- merge(prod_data_compounds,lex_freqs,by="lexeme") %>%
  mutate(neutrality_binary = ifelse(neutrality=="true",1,0)) %>%
  filter(morph_type == "compound") %>%
  mutate(cgender_total = scale(gender_total)) %>%
  mutate(response_congruency = as.numeric(ifelse(congruency=="true","1","0"))) %>%
  mutate(cage = scale(subject_information.age)) %>%
  mutate(cmean_left_neutral = scale(mean_left_neutral)) %>%
  mutate(mean_all = (mean_left_neutral + mean_right_neutral)/2) %>%
  mutate(cmean_all = scale(mean_all))
```

```{r}
freq_model <- lmer(response_neutral~indi_mean + gender.x + poli_party + gender_trans + right_surprisal +  (1|workerid) + (1|name) + (1|lexeme) + (1|subject_information.age), data=join_test)
```

```{r}
summary(freq_model)
```

## Prop Tables

```{r}
(table(prod_data$subject_information.gender))
```



```{r}
prod_gender_table <- prod_data %>%
  group_by(workerid,subject_information.gender,poli_party) %>%
  summarise(subject_gender = paste(unique(subject_information.gender)))

table(prod_gender_table$subject_gender,prod_gender_table$poli_party)
```

```{r}
prod_data_means <- prod_data %>%
  filter(!is.na(poli_party)) %>%
  filter(poli_party != "Non-Partisan") %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>%
  filter(gender!="filler" & gender!= "attention" & gender!="") %>%
  group_by(gender,workerid,poli_party,subject_information.gender,subject_information.age,subject_information.education,gender_total) %>%
  summarise(proportion = mean(response_neutral)) 
```

```{r}
table(prod_data_means$proportion,prod_data_means$poli_party,prod_data_means$gender)
```

## Flight Attendant Case Study

```{r}
final_dat_flight <- final_dat %>%
  filter(lexeme=="flight attendant")
```

```{r}
production_model_flight <- lmer(neutrality_binary~gender + (1|name), data=final_dat_flight)
```

```{r}
summary(production_model_flight)
```

```{r}
flight_attendant <- prod_data %>%
  filter(lexeme == "flight attendant") 
```

```{r}
t.test(response_neutral ~ gender, flight_attendant)
```


```{r}
prod_data %>%
  filter(!is.na(poli_party)) %>%
  filter(lexeme == "flight attendant") %>%
  mutate(response_neutral = ifelse(response_gender == "neutral",1,0)) %>%
  group_by(gender) %>%
  summarize(mean_prop = mean(response_neutral), CI.Low = ci.low(response_neutral), CI.High = ci.high(response_neutral)) %>%
  mutate(YMin = mean_prop - CI.Low, YMax = mean_prop + CI.High) %>%
  ggplot(aes(x=gender,y=mean_prop,fill=gender)) + 
  geom_bar(stat='identity') + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25) + 
  theme_bw() + 
  labs(x="Stimulus Gender", y="Mean Proportion of Neutral Responses",title="Flight Attendant Neutral Responses by Stimuli Gender") + 
  theme(text=element_text(size=16)) + 
  theme(axis.text.x = element_text(angle=5, vjust = .7)) + 
  scale_fill_manual(values = bran_palette) +
  theme(legend.position = "none")
```



