---
title: "Analysis of Norming Study Results"
author: "Bran Papineau"
output: html_notebook
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(data.table)
library(formattable)
library(grid)
```

# Data Read-ins

## Reading in the .csv file & prepping data for grouping:


This reads in the .csv file with the data from all 4,000 trials:

```{r}
trials <- read.csv("gender_titles-merged.csv")
```

This will filter out example trials + the respondent who reported not understanding: 

```{r}
real_trials <- trials %>%
  filter(id!="example1") %>% 
  filter(workerid!=76)
```


This will unify all data, regardless of the scale they were conducted on:

Brute force:
```{r}
final_trials_ugly <- real_trials %>%
  mutate(new_response = ifelse(scale=="FM"&response==1,7,ifelse(scale=="FM"&response==2,6,ifelse(scale=="FM"&response==3,5, ifelse(scale=="FM"&response==5,3, ifelse(scale=="FM"&response==6,2, ifelse(scale=="FM"&response==7,1,ifelse(scale=="FM"&response==4,4,response))))))))
```

Much cleaner:
```{r}
trials_final <- real_trials %>% 
  mutate(equalized_response = ifelse(scale=="FM",8-response,response))
```

Now we can run the exclusion criteria:

```{r}
trials_final %>% 
  filter(gender=="female") %>% 
  group_by(workerid) %>%
  summarize(female_mean = mean(equalized_response)) %>%
  unique() %>% 
  mutate(exclusion = female_mean < mean(female_mean) - 2*sd(female_mean)) %>%
  filter(exclusion==TRUE)
```

And exclude those participants whose ratings fall outwith the exclusion criterion: 

```{r}
usable_trials <- trials_final %>%
  filter(workerid!=17 & workerid!=35 & workerid!=54 & workerid!=57 & workerid!=68 & workerid!=69 & workerid!=72 & workerid!=86 & workerid!=89 & workerid != 107 & workerid != 111) %>%
  mutate(orthog = ifelse(orthog=="sroceress","sorceress",orthog)) %>%
  mutate(id = ifelse(id=="Stunt_double","Stunt double",id)) %>%
  mutate(id = ifelse(id=="Restaurant_server","Restaurant server",id)) %>%
  mutate(id = ifelse(id=="Police_officer","Police officer",id)) %>%
  mutate(id = ifelse(id=="Door_attendant","Door attendant",id)) %>%
  mutate(id = ifelse(id=="Flight_attendant","Flight attendant",id)) %>%
  mutate(id = ifelse(id=="Garbage_Collector","Garbage collector",id)) %>%
  mutate(id = ifelse(id=="Mail_Carrier","Mail carrier",id)) %>%
  mutate(id = ifelse(id=="Maintenance_Person","Maintenance person",id)) %>%
  mutate(id = ifelse(id=="Paper_carrier","Paper carrier",id))
```


# Analysis

```{r}
inauguration_2021 = c("#5445b1", "#749dae", "#f3c483", "#5c1a33", "#cd3341","#f7dc6a")
```

### Means by Item

```{r}
underlying <- usable_trials %>%
  group_by(id,gender,orthog) %>%
  summarise(indi_mean = mean(equalized_response), trial_count=n())
```

```{r}
text_high <- textGrob("Female", gp=gpar(fontsize=10, fontface="bold"))
text_low <- textGrob("Male", gp=gpar(fontsize=10, fontface="bold"))
```


```{r}
ggplot(underlying, aes(x=id, y=indi_mean, color=gender)) + 
  geom_point() + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=45, hjust=1, size=8)) + 
  labs(x="Ungendered Lexical Item", y="Mean Rating", color = "Gender of Form", title="Mean Gender Rating by Ungendered Form and Gender Seen") + 
  scale_color_manual(values = inauguration_2021) + 
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  annotation_custom(text_high,xmin=-1.3,xmax=-1.3,ymin=7,ymax=7) + 
  annotation_custom(text_low,xmin=-1,xmax=-1,ymin=1,ymax=1) + 
  coord_cartesian(clip = "off")
```
```{r}
ggsave(height=4,width=7,path="/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper",filename="norming_values.png")
```


```{r}
collapsed_means <- usable_trials %>%
  group_by(orthog) %>%
  summarize(mean(equalized_response)) %>%
  rename(
    'Orthographic Form' = "orthog",
    'Mean Gender Value' = "mean(equalized_response)"
  )
```


### Setting custom colours for the formattable table

```{r}
custom_pink = "#FFB6C1"
custom_blue = "#ADD8E6"
```


```{r}
collapsed_means %>%
  formattable(align= c('l','r'),
            list('orthog' = formatter("span", style = ~style(color = "grey", font.weight="bold")),
            "Mean Gender Value" = color_tile(custom_blue, custom_pink)))
```

## Means by Morphological Processes

### Means by Gendered Morphology

```{r}
morphological_means <- usable_trials %>%
  group_by(gendered_morph,gender) %>% 
  summarize(morph_mean = mean(equalized_response), trial_sum = n())
```

```{r}
ggplot(morphological_means, aes(x=gendered_morph, y=morph_mean, color=gender, size=trial_sum)) + 
  geom_point() + 
  theme_minimal() + 
  labs(x="Gender Marking Processes", y="Mean Rating", size="Number of Observations", color="Gender") + 
  scale_x_discrete(labels=c("Boy/Girl Compound","Other Gender Compound","Man/Woman Compound","Suffix")) + 
  theme(axis.text.x = element_text(angle=15))
```

### Means by Gender Neutral Morphology

```{r}
neutral_means <- usable_trials %>%
  group_by(neutral_morh,gender) %>% 
  summarize(neutral_mean = mean(equalized_response), trial_sum = n())
```
```{r}
ggplot(neutral_means, aes(x=neutral_morh, y=neutral_mean, color=gender, size=trial_sum)) + 
  geom_point() + 
  theme_minimal() + 
  labs(title="Mean Gender Evaluation by Neutral-Form Derivation Process", x="Neutral Formation Process", y="Mean Rating", size="Number of Observations", color="Gender") + 
  scale_color_manual(values=inauguration_2021) + 
  scale_x_discrete(labels=c("Clipping", "Male Adoption", "Neutral Compound", "Person Compound", "Suppletion")) + 
  theme(axis.text.x = element_text(angle=15)) + 
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  annotation_custom(text_high,xmin=.3,xmax=0.3,ymin=6.6,ymax=6.6) + 
  annotation_custom(text_low,xmin=.3,xmax=.3,ymin=2.4,ymax=2.4) + 
  coord_cartesian(clip = "off")
```

```{r}
ggsave(height=4,width=7,path="/Users/branpap/Desktop/gender_processing/talks_and_papers/qp_paper",filename="norming_deriv.png")
```

## Calculating the Mean Number of Times an Item Was Seen

```{r}
mean(underlying$trial_count)
```

```{r}
summary(trials)
```


