---
title: "Analysis of Norming Study Results"
author: "Bran Papineau"
output: html_notebook
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(data.table)
library(formattable)
```

# Data Read-ins

## Reading in the .csv file & prepping data for grouping:


This reads in the .csv file with the data from all 4,000 trials:

```{r}
trials <- read.csv("gender_titles-trials.csv")
```

This will filter out example trials + the respondent who reported not understanding: 

```{r}
real_trials <- trials %>%
  filter(id!="example1") %>% 
  filter(workerid!=76)
```


This will unify all data, regardless of the scale they were conducted on:

Brute force:
```{r}
final_trials_ugly <- real_trials %>%
  mutate(new_response = ifelse(scale=="FM"&response==1,7,ifelse(scale=="FM"&response==2,6,ifelse(scale=="FM"&response==3,5, ifelse(scale=="FM"&response==5,3, ifelse(scale=="FM"&response==6,2, ifelse(scale=="FM"&response==7,1,ifelse(scale=="FM"&response==4,4,response))))))))
```

Much cleaner:
```{r}
trials_final <- real_trials %>% 
  mutate(equalized_response = ifelse(scale=="FM",8-response,response))
```

Now we can run the exclusion criteria:

```{r}
trials_final %>% 
  filter(gender=="female") %>% 
  group_by(workerid) %>%
  summarize(female_mean = mean(equalized_response)) %>%
  unique() %>% 
  mutate(exclusion = female_mean < mean(female_mean) - 2*sd(female_mean)) %>%
  filter(exclusion==TRUE)
```

And exclude those participants whose ratings fall outwith the exclusion criterion: 

```{r}
usable_trials <- trials_final %>%
  filter(workerid!=17 & workerid!=35 & workerid!=54 & workerid!=57 & workerid!=68 & workerid!=69 & workerid!=72 & workerid!=86 & workerid!=89 & workerid != 107 & workerid != 111) %>%
  mutate(orthog = ifelse(orthog=="sroceress","sorceress",orthog)) 
  
```


# Analysis

### Means by Item

```{r}
underlying <- usable_trials %>%
  group_by(id,gender,orthog) %>%
  summarise(indi_mean = mean(equalized_response), trial_count=n())
```

```{r}
ggplot(underlying, aes(x=id, y=indi_mean, color=gender)) + 
  geom_point() + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle=45, hjust=1, size=8)) + 
  labs(x="Ungendered Lexical Item", y="Mean Rating", color = "Gender of Form", title="Mean Gender Rating by Ungendered Form and Gender Seen")
```


```{r}
collapsed_means <- usable_trials %>%
  group_by(orthog) %>%
  summarize(mean(equalized_response)) %>%
  rename(
    'Orthographic Form' = "orthog",
    'Mean Gender Value' = "mean(equalized_response)"
  )
```


### Setting custom colours for the formattable table

```{r}
custom_pink = "#FFB6C1"
custom_blue = "#ADD8E6"
```


```{r}
collapsed_means %>%
  formattable(align= c('l','r'),
            list('orthog' = formatter("span", style = ~style(color = "grey", font.weight="bold")),
            "Mean Gender Value" = color_tile(custom_blue, custom_pink)))
```

## Means by Morphological Processes

### Means by Gendered Morphology

```{r}
morphological_means <- usable_trials %>%
  group_by(gendered_morph,gender) %>% 
  summarize(morph_mean = mean(equalized_response), trial_sum = n())
```

```{r}
ggplot(morphological_means, aes(x=gendered_morph, y=morph_mean, color=gender, size=trial_sum)) + 
  geom_point() + 
  theme_minimal() + 
  labs(x="Gender Marking Processes", y="Mean Rating")
```

### Means by Gender Neutral Morphology

```{r}
neutral_means <- usable_trials %>%
  group_by(neutral_morh,gender) %>% 
  summarize(neutral_mean = mean(equalized_response), trial_sum = n())
```
```{r}
ggplot(neutral_means, aes(x=neutral_morh, y=neutral_mean, color=gender, size=trial_sum)) + 
  geom_point() + 
  theme_minimal() + 
  labs(x="Neutral Formation Process", y="Mean Rating")
```

## Calculating the Mean Number of Times an Item Was Seen

```{r}
mean(underlying$trial_count)
```



