---
title: "Merge to the Berge"
output: html_notebook
---
```{r}
library(tidyverse)
library(brms)
```

```{r}
inauguration_2021 = c("#5445b1", "#749dae", "#f3c483", "#5c1a33", "#cd3341","#f7dc6a")
bran_palette = c("#7ae7e5", "#fe5f55", "#B2A6DE", "#14342b", "#69385c")
sec_palette = c("#3d405b","#e07a5f","#81b29a","f2cc8f")
```

```{r}
#maze <- read.csv("merged_all_maze.csv")
spr <- read.csv("merged_all_spr.csv") %>%  
  mutate(poli_party = ifelse(subject_information.party_alignment == 1 | subject_information.party_alignment == 2,'Republican',ifelse(subject_information.party_alignment == 4 | subject_information.party_alignment == 5,'Democrat','Non-Partisan')))

prod <- read.csv("merged_all_prod.csv") %>% 
  mutate(poli_party = ifelse(subject_information.party_alignment == 1 | subject_information.party_alignment == 2,'Republican',ifelse(subject_information.party_alignment == 4 | subject_information.party_alignment == 5,'Democrat','Non-Partisan')))
```

```{r}
gender_transcendence_cols <- c('subject_information.gender_q1','subject_information.gender_q2','subject_information.gender_q3','subject_information.gender_q4','subject_information.gender_q5')

gender_linked_cols <- c('subject_information.gender_q6','subject_information.gender_q7','subject_information.gender_q8','subject_information.gender_q9','subject_information.gender_q10','subject_information.gender_q11','subject_information.gender_q12','subject_information.gender_q13')
```


maze <- maze %>%
  mutate(gender_trans = 100 - (rowMeans(maze[gender_transcendence_cols]))) %>%
  mutate(gender_link = rowMeans(maze[gender_linked_cols])) 

gender_all = c('gender_trans','gender_link')

maze <- maze %>%
  mutate(gender_total = rowMeans(maze[gender_all])) %>%
  group_by(workerid) %>%
  summarize(gt = paste(unique(gender_total)),gender = paste(unique(subject_information.gender)),experiment="Maze") 

```{r}
spr <- spr %>%
  mutate(gender_trans = 100 - (rowMeans(spr[gender_transcendence_cols]))) %>%
  mutate(gender_link = rowMeans(spr[gender_linked_cols])) 

gender_all = c('gender_trans','gender_link')

spr <- spr %>%
  mutate(gender_total = rowMeans(spr[gender_all])) %>%
  group_by(workerid,poli_party,subject_information.age) %>%
  summarize(gt = paste(unique(gender_total)),gender = paste(unique(subject_information.gender)),experiment="Self-Paced Reading",gender_linked = paste(unique(gender_link)), gender_trans = paste(unique(gender_trans)), age = paste(unique(subject_information.age)))
```

```{r}
prod <- prod %>%
  mutate(gender_trans = 100 - (rowMeans(prod[gender_transcendence_cols]))) %>%
  mutate(gender_link = rowMeans(prod[gender_linked_cols])) 

gender_all = c('gender_trans','gender_link')

prod <- prod %>%
  mutate(gender_total = rowMeans(prod[gender_all])) %>%
  group_by(workerid,poli_party) %>%
  summarize(gt = paste(unique(gender_total)),gender = paste(unique(subject_information.gender)),experiment="Production",gender_linked = paste(unique(gender_link)), gender_trans = paste(unique(gender_trans)), age = paste(unique(subject_information.age)))
```

```{r}
ideology <- rbind(prod,spr) %>% 
  select(-c("subject_information.age"))
```


#```{r}
#cons_text <- textGrob("Conservative", gp=gpar(fontsize=10, fontface="bold"))
#lib_text <- textGrob("Liberal", gp=gpar(fontsize=10, fontface="bold"))
#```

```{r}
ideology %>%
  filter(gender != "") %>%
  ggplot(aes(x=gender, y=as.numeric(gt), fill=gender)) + 
  geom_boxplot() + 
  theme_minimal() + 
  facet_wrap(~experiment) + 
  labs(x="Participant Gender", y="Gender Ideology Score") + 
  theme(legend.position = 'none') + 
  scale_fill_manual(values=inauguration_2021)
```

```{r}
ggsave(height=4,width=7,path="/Users/branpap/Desktop/gender_ideology/talks_and_papers/qp_paper",filename="merge_ideo_pure.png")
```


```{r}
ideology %>%
  filter(poli_party != "") %>%
  ggplot(aes(x=poli_party, y=as.numeric(gt), fill=poli_party)) + 
  geom_boxplot() + 
  theme_minimal() + 
  labs(x="Participant Poliitcal Party", y="Gender Ideology Score") + 
  theme(legend.position = 'none') + 
  scale_fill_manual(values=bran_palette, limits=c("Democrat","Republican","Non-Partisan")) + 
    theme(text=element_text(size=14))
```

```{r}
ggsave(height=4,width=7,path="/Users/branpap/Desktop/gender_ideology/talks_and_papers/qp_paper",filename="merge-ideo.png")
```


```{r}
ideology <- ideology %>% 
  mutate(gender_linked = as.numeric(gender_linked)) %>% 
  mutate(gender_trans = as.numeric(gender_trans)) %>% 
  mutate(gt = as.numeric(gt)) %>% 
  mutate(age = as.numeric(age)) %>% 
  mutate(young_old = case_when(
    age >= 40 ~ "old",
    age < 40 ~ "young"
  ))
```


```{r}
ideology %>% 
  filter(!is.na(poli_party)) %>% 
  ggplot(aes(x=gender_trans,y=gender_linked,color=poli_party)) + 
  geom_point(alpha = 0.2) + 
  theme_minimal() + 
  stat_ellipse(aes(color=poli_party)) + 
  labs(x = "Gender Transcendence", y="Gender Linking", color = "Political Party") + 
  scale_color_manual(values=bran_palette, limits=c("Democrat","Republican","Non-Partisan")) + 
  theme(text=element_text(size=14))
```

```{r}
ideology %>% 
  filter(!is.na(poli_party)) %>% 
  filter(gender != "") %>% 
  ggplot(aes(x=gt, color=poli_party,fill=poli_party)) + 
  geom_density(alpha = 0.3) + 
  facet_wrap(~gender) + 
  theme_bw() + 
  labs(x = "Gender Total", fill = "Political Party", color = "Political Party") + 
  scale_color_manual(values=bran_palette, limits=c("Democrat","Republican","Non-Partisan")) + 
  scale_fill_manual(values=bran_palette, limits=c("Democrat","Republican","Non-Partisan"))
```

3 Models for Bayesian Analysis:

Null Model: gt ~ 1
Simple Model: gt ~ poli_party + (1|worker.id)

```{r}
get_prior(gt ~ poli_party + (1|workerid), data = ideology, family = gaussian())
```


### Age

```{r}
ideology %>% 
  ggplot(aes(x = age, fill=gender)) + 
  geom_bar() +
  theme_bw() + 
  scale_fill_manual(values = bran_palette, limits=c("Male","Female","Other","Unknown")) + 
  facet_wrap(~experiment)
```

```{r}
table(ideology$young_old, ideology$poli_party,ideology$experiment)
```


```{r}
mean(ideology$age, na.rm = TRUE)
```

```{r}
mean(as.numeric(prod$age), na.rm=TRUE)
```

```{r}
mean(as.numeric(spr$age), na.rm=TRUE)
```



